---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FoodWebDentriticNetwork

<!-- badges: start -->
<!-- badges: end -->

The goal of FoodWebDentriticNetwork is to ...

## Explain ouput web_in_web.rda 

- `fish_length`: individual fish bodysize 
- `metaweb`: list of `metaweb`, `species` and `resources` 
- `network`: networks for each sampling events 
- `com_species`, `com_trophic_species`: metric at scale of species and trophic
  species (e.g. biomass and number of individuals) 
- `com_metrics`, `network_metrics`: metrics at community and network scale
- `network_mat`
- `op_st_filtered`: list of "station", "op", "op_desc", "op_env" (site
  information and sampling information)
- `riveratlas_station`: collection of hydro-morpho, climatic variables for
  RiverAtlas

# load data 

```{r, eval=FALSE}
load("web_in_web.rda")
```
