---
title: "Betadiversity in dentritic network"
author: "Alain Danet"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, out.width = "100%")
## target knits Rmds in their own session, so load libraries here.
## source("here::here(packages.R"))
library(cowplot)
theme_set(theme_half_open())
```

```{r load-targets, include=FALSE}
tar_load(c(p_beta_site_versus_all_ord_stra,
p_beta_site_versus_all_width, p_beta_by_width, p_beta_site_by_stra
))
# tar_load(c(target_1, target_2, target_3))

# # If your chunk output is shown in-line, then you'll need to wrap tar_load()
# # like so:
# 
# withr::with_dir(here::here(), {
#   tar_load(c(target_1, target_2, target_3))
# })
# 
# # This is not needed when using tar_make() to render the document.
```
# Methods

We aggregated community composition by site, considering that a species was
present if it occurred in more than 10% of the sampling in a given site.

Spatial dissimilarity was computed with the Jaccard index using `betapart` R
package. We also computed partitions of the Jaccard dissimilarity index in
nestedness (nested composition) and turnover (species replacement).

# Betadiversity one site versus all 

In this case, we computed average dissimilarity of each site with all the other
sites in the each basin.

```{r, fig.width = 10, fig.asp = .6}
p_beta_site_versus_all_ord_stra
p_beta_site_versus_all_width
```

# Betadiversity one site versus all

In this case, we computed average dissimilarity among sites belonging to the
same strahler order or to the same river width category. 

```{r, fig.width = 11, fig.asp = .6}
p_beta_site_by_stra
p_beta_by_width +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

## Reproducibility

<details><summary>Reproducibility receipt</summary>

```{r}
## datetime
Sys.time()

## repository
if(requireNamespace('git2r', quietly = TRUE)) {
  git2r::repository()
} else {
  c(
    system2("git", args = c("log", "--name-status", "-1"), stdout = TRUE),
    system2("git", args = c("remote", "-v"), stdout = TRUE)
  )
}

## session info
sessionInfo()
```

</details>
